decide what needs to be optimized;
run a profiler, pycharm has a profiler.

Many categorical variables, linear regression
will throw a fit without regularization.

Confusion matrix has every possible metric under the sun

null hypothesis testing?

practical point of view; create
a custom cost function, make it specific
to your project or

confusion matrix wikipedia page.

hairy hand; anecdote? design
guys in animation. In order cartoons,
a rule was don't put hair on hands.
This was about logistic regression and
classification.

For linear regression.
In business need to communicate $R^2$.
How do you apply r squared if you're talking about something else that is not
based on regression? It's always
going to work is the correlation between
the actual versus predicted, get this and
square it (assumes error is additive) to have a r squared type measure. absolute errors in time series. How to compare new versus past?

actual versus predicted.  mean root square error.

It takes time to agree on a metric. People start talking about model
performance of ninety percent. Not talking about some sort of accuracy or r squared, they are talking about a bias, like combining certain metrics. If on average you are on target. It's not relavant and Mike called them out on it. A lot of communication going on, terms are defined properly, need to adapt to what is needed for
the project, what you're trying to improve, predict, 
produce. This is where data scientists are not going to
be replaced by automation. Explaining it to people is
the main job. 

glmnet
elasticnet