Are models that do not converge but perform well invalid?
My answer is absolutely they are not valid. 


Does reference to data in the past result in snooping?
How to handle values which contain aggregated time data. Like number of delinquent accounts in
past two years?

Regarding the time series rows/columns. Information about the borrower. 
Take the past and summarize it for that particular information. 
Can make up stuff about the history; it's like a summary statistic. 

More important for time that the decision is being made. 
Nothing from the future. Can only reference information that
is available at the time of decision. Think about fitbit/whoop
heart rate or even phone with accelerometer; there are multiple
data points in the interval of measurement. 

convention of labeling good/bad as 0/1

Any imputation; include dummy column; imputed or not. 

######
Only use the continuous data for continuous regression?

amount of money to be retrieved from charged off loans; remove all but
charged off loans? outcome of loan, remove current loans ?

---One hot encoding 
What stops you from shuffling the category codes; there is permutation
symmetry. 

Idiosyncratic responses: create tokens, extract the root word and
eliminate the stop words. From that list assign values to words. Vector
auto encoding. Simple feature just do word count, sentiment, etc. Natural
Language processing. 

NLTK.

Only use regression on values greater than zero for recoveries?

If trying to predict the amount of money recovered from charged-off loans should only the charged-off loan data be used?

It depends on the time-frame. Can make my own time frame. If I do this
I can decide on the time frame. Need to take the time frame into account.

When do you consider your data to be a population versus a sample?
Metric based on the null rate. 

random/unimportant
Subdivision into "neat"/"pretty" intervals; isn't this actually a bad thing to do?
depends on interpretation/presentation?

Draw questions to convince yourself. 

with correlation there is some (small) new information, so 
RFE
This is why deep learning and big data is successful. 

RFE, PCA isn't that useful when compared to L2 

should you use categorical variables in linear regression?

should you use continuous variables in classification?

how careful do you need to be when taking subsets of features?
is this ever done manually?

Conversion of variable to categorical where number of categories is incredibly large?

become paranoid about touching data. 