\subsection{Tanya Kuwadekar(1) Wednesday, December 12th 2019}


How many of these meetings?

\subsubsection{LinkedIn}
Really bad at this and social media in general.

Keep about section as very to the point.
In addition to that want to make sure
that building my brand as someone who is.

Don't want to be

Do certain things in profile will have recruiters
reaching out. Want to have LinkedIn. Want
LinkedIn to be like a resume. 

"Theme", what are your Physics. 

This is your background, think of this as your resume.
Don't  want it to

Want projects, "data scientist", description of springboard, don't 

Want the right keywords. Want to reach out to people
I don't know. Want more honest connections. 

List of keywords that she can share. LinkedIn profiles
are based on the end result. Want to lean on referrals
and connections. Direct applications taking time
to send resume. Want profile to work for me, recruiters messaging me.

Want to diversify my profile to combine all of these 
Recruiters go through the bucket once or twice a month,
going through hundreds of profiles but if coworkers send
a resume it'll be 

Going into the skill section she can show how recruiters look through profile. 

Recruiter profile is much more basic. 

Looking at headline, summary, skills, expertise. 

Want to be in the segment of people who show up in searches. Headline and current job and past all say data
scientist. 

Add data scientist and student at springboard. 
Put "data science career track"
Always recommend writing "Data Scientist"

If you start applying to positions, LinkedIn, indeed.

Easy to find positions and do keyword searches. Going to create a strategy for me because I don't have 

Want to make sure the technical side experience is there before anything else. Want words and content on profile to match specific industry standards.

Harder to break into industry but once you do it starts to have projects and phrases that correspond to data science. 
Explaining things in a certain way that the audience can
relate to.
Statistical modeling or statistical data analysis.

% I tend to write as if 

Don't really care to find someone with personal skills.
No time to find or read about interpersonal skills 

"Soft skills" are mainly through 

Add springboard and data scientist student 
Describing projects under springboard.
Sending list of keywords via skype. 
List top ten skills definitely, depends on the keyword
Put on resume things you can defend but keep LinkedIn
Only Fill up LinkedIn skills and expertise 
One per month career meeting. 


\subsubsection{Other}