Are models that do not converge but perform well invalid?

Can you argue that time series data that isn't exclusively linked to other time series values
(i.e. single instance time variables).

The issued dat of loans are discrete stamps which do not track a variable.
The only issue at hand is if the company itself used old data to predict new data which
determined who got new loans.

Ignoring historical context; like 2008 financial crisis.

Does reference to data in the past result in snooping?
How to handle values which contain aggregated time data. Like number of delinquent accounts in
past two years?

amount of money to be retrieved from charged off loans; remove all but
charged off loans?

outcome of loan, remove current loans ?

single value?

continuous data only for continuous regression?

Isn't my case different;

Instead of a sequence of values X_1, X_2, X_3, ...
there are instead samples which occur at a certain time, as well as references to the past.
The present value of a window of the past. 

If handling outcomes, should only use loans which have concluded?

If trying to predict the amount of money recovered from charged-off loans should only the
charged-off loan data be used?

When do you consider your data to be a population versus a sample?

Subdivision into "neat"/"pretty" intervals; isn't this actually a bad thing to do?
depends on interpretation/presentation?

should you use categorical variables in linear regression?

should you use continuous variables in classification?

how careful do you need to be when taking subsets of features?
is this ever done manually? 

Conversion of variable to categorical where number of categories is incredibly large?

become paranoid about touching data.