\subsection{Unit 7 Notes: Data Storytelling September 21th 2019}

\subsubsection{Bad visualizations}
Offload your mental processes onto the visualization;
see patterns without thinking very hard. WTF visualizations
have a good examples of bad visualizations.

Effective visualizations have
\begin{itemize}
\item graphical integrity
\item simplicity
\item right display
\item use color strategically
\item tell a story with data
\end{itemize}

Maximize Data-ink ratio. Pretty
doesn't matter; focus on the data.
three dimensional visualization are bad.

Great flow chart for different types
of intentions.

\subsubsection{Comparison}
\textbf{Between items} \\
\begin{itemize}
\item Variable width column chart (two variables per item)
\item Table or Table of Charts (many categories, single variable)
\item Bar charts, column charts (few categories, single variable)
\end{itemize}

\textbf{Over time} \\
\begin{itemize}
\item Circular area chart (cyclical data, many periods)
\item Line chart (non-cyclical, many periods)
\item Column chart (single,few categories; few periods)
\item Line chart (many lines) (many categories, few periods)
\end{itemize}

\subsubsection{Distribution}
\begin{itemize}
\item Column histogram (few data points, single variable)
\item Line histogram (many data points, many varibels
\item Scatter chart (Two variables)
\item ThreeD area chart (Three variables)
\end{itemize}

\subsubsection{Composition}
\textbf{Changing over time} \\
\begin{itemize}
\item stacked, 100 percent column chart (relative difference matter, few periods)
\item stacked column chart (relative and absolute differences matter, few periods)
\item stacked 100 percent area chart (only relative differences matter, many periods)
\item stacked area chart (relative and absolute matter, many periods)
\end{itemize}

\textbf{Static} \\
\begin{itemize}
\item 2D pie chart (Simple share of total)
\item Waterfall chart (Accumulation or subtraction to total)
\item Stacked 100 percent column chart with subcomponents (components of components)
\item
\end{itemize}

\subsubsection{Relationship}
\begin{itemize}
\item Scatter chart (two variables)
\item Bubble chart (three variables)
\end{itemize}

Each visualization is good at answering a
single question. Sometimes a single number is the
best way of answering questions succinctly.

What is the goal? Who cares?
IMAC, inferential goa, model, algorithms, conclusions and checking.
Golden rules, know your audience, tell a story, choose a notation
carefully. read great writers. Create a clear sense of direction,
with the help of signposts, with clear flow of logic.
(here's what we've done, here's where we are, where we're going.)

The science of scientific writing Gopen-swan
Linda the bank teller (kahneman tversky).
Tell a story
\begin{itemize}
\item interesting characters
\item predicament
\item resolve the predicament
\item leave room for sequels
\end{itemize}

Successful Data stories
\begin{itemize}
\item target the audience
\item engage and are memorable
\item answer concise questions
\item are carefully designed
\item move us to want to change the world
\end{itemize}



